Technical Report

### 2017-10-27 fully-abstract-comp/technical-report.tex
typos

Disjoint union of worlds. Joins together two alike worlds with strictly disjoint ownership over $\pureReg$-regions.
\[
  W_1 \uplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (i,\normalReg,\var{sm}) \uplus (j,\normalReg,\var{sm}) =  & \; (\max(i,j),\normalReg,\var{sm}) \\
  (1,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) =      & \; (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (1,\pureReg,\var{sm}) =      & \; (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) =      & \; (0,\pureReg,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\uplus$ is not defined when both sides are an owned $\pureReg$-region. It is further not defined if the two sides do not agree on region type and state machine.

>>>>

Disjoint union of worlds. Joins together two alike worlds with strictly disjoint ownership over $\pureReg$-regions.
\[
  W_1 \uplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (i,\normalReg,\var{sm}) \oplus (j,\normalReg,\var{sm}) =  & \; (\max(i,j),\normalReg,\var{sm}) \\
  (1,\pureReg,\var{sm}) \oplus (0,\pureReg,\var{sm}) =      & \; (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \oplus (1,\pureReg,\var{sm}) =      & \; (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \oplus (0,\pureReg,\var{sm}) =      & \; (0,\pureReg,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\oplus$ is not defined when both sides are an owned $\pureReg$-region. It is further not defined if the two sides do not agree on region type and state machine.
